### 2011-02-25 trunk/deliverables/D5_1_2/fast_d5_1_2.tex
fixes a typo
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1300 d8b0c59b-6544-0410-94d9-83a5658a058e

This sections enumerates and gives a brief overview of the changes made in the deliverable with regards to the version 1.0 released for the milestone M24.

>>>>

This section enumerates and gives a brief overview of the changes made in the deliverable with regards to the version 1.0 released for the milestone M24.
